---
title: "Set12_DESeq2_snATAC_with_bulkATAC_peak_counts"
output:
  html_document: default
  pdf_document: default
---

```{r, message=F, warning=F}
library(DESeq2)
library(dplyr)
library(tidyr)
library(pheatmap)
library(pals)
library(ggplot2)
library(ggrepel)
library(stringr)
```

# Read in table from DiffBind_ATACseq_bulkATACseq_counts.R and tidy
```{r}
counts <- read.csv("output/Set12_snATACseq_bulkATAC_celltype_counts_summ.csv", header = T, row.names = NULL)
```

## Unite peak coordinates into one column, convert to row.names
```{r}
counts.t <- unite(counts, "coord", START:END, sep = "-")
counts.t <- unite(counts.t, "peak_coord", CHR:coord, sep = "-")
colnames(counts.t) <- sub("_", ".", colnames(counts.t))

cts <- as.matrix(tibble::column_to_rownames(counts.t, var = "peak.coord"))
```

# Make metadata table
```{r}
population <- colnames(cts)

celltype <- factor(c(rep("Oligodendrocyte", 2),
                     "Glutamatergic Neuron",
                     "Astrocyte",
                     "Microglia",
                     "Oligodendrocyte Precursor Cell",
                     "Glutamatergic Neuron",
                     rep("GABAergic Neuron", 2),
                     rep("Glutamatergic Neuron", 2),
                     "GABAergic Neuron",
                     "Glutamatergic Neuron",
                     "GABAergic Neuron",
                     "Astrocyte",
                     "Vascular Cell",
                     rep("Glutamatergic Neuron", 4),
                     "GABAergic Neuron",
                     "Glutamatergic Neuron",
                     rep("iMicroglia", 4),
                     rep("iFbN", 3)))

source <- factor(c(rep("Brain_FC", 22), rep("iPSC_PPMI", 4), rep("iPSC_33i", 3)))

coldata <- data.frame(population, celltype, source)
coldata <- tibble::column_to_rownames(coldata, var = "population")
```

```{r}
all(rownames(coldata) %in% colnames(cts))
all(rownames(coldata) == colnames(cts))
```

# Check out data
```{r, message=F, warning=F}
dds <- DESeqDataSetFromMatrix(countData = cts, colData = coldata, design = ~ celltype)
dds
```

# Normalize and transform counts for data visualization
### If the library size of the samples and therefore their size factors vary widely, the rlog transformation is a better option than VST. Both options produce log2 scale data which has been normalized by the DESeq2 method with respect to library size
```{r, message=F, warning=F}
dds <- estimateSizeFactors(dds)
rld <- rlog(dds, blind = TRUE)
```

## PCA
```{r, fig.width=10, fig.height=5}
plotPCA(rld, intgroup = "celltype")
```

## hierarchical clutsering
```{r, fig.width=8, fig.height=6}
rld.mat <- assay(rld)
rld.cor <- cor(rld.mat)
rld.cor
```

```{r}
rld.df <- as.data.frame(rld.mat)

ct.iMGL.3411vsMGL.4 <- cor.test(rld.df$iMGL.3411, rld.df$MGL.4, method = "pearson")
print(ct.iMGL.3411vsMGL.4, digits = 10)
```

```{r, fig.width = 10, fig.height = 7}
newCols <- colorRampPalette(pals::alphabet2(length(unique(coldata$celltype))))
mycolors <- newCols(length(unique(coldata$celltype)))
names(mycolors) <- unique(coldata$celltype)

newCols2 <- colorRampPalette(pals::alphabet(length(unique(coldata$source))))
mycolors2 <- newCols2(length(unique(coldata$source)))
names(mycolors2) <- unique(coldata$source)


mycolors <- list(celltype = mycolors, source = mycolors2)

p1 <- pheatmap(rld.cor, annotation = coldata,
         color = hcl.colors(12, "Plasma"),
         border_color = NA,
         fontsize = 10, fontsize_row = 10, height=20,
         annotation_colors = mycolors)

#ggsave("plots/DESeq2_snATACseq_vs_bulkATACseq_heatmap.png", plot = p1, width = 10, height = 7)
#ggsave("plots/DESeq2_snATACseq_vs_bulkATACseq_heatmap.svg", plot = p1, width = 10, height = 7)
p1
```





